Evolution plots

### 2016-02-29 scrap/evolution.Rmd
old data cleanup and scrap changes

---
title: "Evolution plots"
author: "John Wilshire"
date: "18 February 2016"
output:
  pdf_document:
    fig_crop: no
    fig_height: 4
  html_document: default
---

@@

```{R}
expf10_pop <- load_population("../data/exp_f10/")
expf15_pop <- load_population("../data/exp_f15/")
linf10_pop <- load_population("../data/lin_f10/")
population_plots <- function (y, x){
  print(pop_values(expf10_pop, x, y, paste("expf10_pop", y)))
  print(pop_values(expf15_pop, x, y, paste("expf15_pop", y)))
  print(pop_values(linf10_pop, x, y, paste("linf10_pop", y)))
}

>>>>

---
title: "Evolution plots"
author: "John Wilshire"
date: "18 February 2016"
output:
  html_document: default
  pdf_document:
    fig_crop: no
    fig_height: 4
---

@@

```{R}
expf10_pop <- load_population("../data/exp_f10/")
expf15_pop <- load_population("../data/exp_f15/")
linf10_pop <- load_population("../data/lin_f10/")
exp10_1000_pop <- load_population("../data/exp_f10_1000/")
population_plots <- function (y, x){
  print(pop_values(expf10_pop, x, y, paste("expf10_pop", y)))
  print(pop_values(expf15_pop, x, y, paste("expf15_pop", y)))
  print(pop_values(linf10_pop, x, y, paste("linf10_pop", y)))
}
